A Control Strategy for a Tethered Follower Robot for Pulmonary Rehabilitation

### 2020-04-18 alpibot.tex
Upload of a new version of the pdf.

On the other hand, several assistance devices for COPD treatments have been proposed.  Particularly relevant are novel telemedice applications to enhance complementary rehabiliation exercise at home that can track biological markers for patients~\cite{Wu2012}.  The work presented here follows the line established by \cite{Endo2015}.  Authors studied the use of a single thread tethered follower robot for home oxygen therapy, and compared two different control algorithms and their effectiveness to mimic the leader path and to avoid obstacles.  However, their approach focuses on the usage of the device exclusively for home therapy, and not within the context of a Pulmonary Rehabilitation procedure performed by medical personnel on medical facilities.

@@

The Raspberry (Raspberry Pi Foundation, United Kingdom) board connects to a WiFi network and can receive remote commands to control the robot. It also broadcasts the telemetry data to any listening devices on the network. The control algorithms run in this board, which continuously communicates with the Arduino board to receive sensor data and to issue commands to move the motors or retract the reels.   The algorithms are programmed in python 3.7, which allows the exact same code to run both the simulated and real world prototype.

@@

\subsection{Software Components}

@@

This control strategy is similar to the one presented in \cite{Ortlieb2016}. It is based on the idea that the difference in length between both threads provides a quasi-linear function of the relative angle between the subject and the vehicle orientation and, additionally, the mean of both thread length allows to approximate the relative distance between the robot and the subject.

@@

\begin{equation}
vleft_{tar} = v_{tar} + c_{\alpha} (D_l - D_r)
\end{equation}

\begin{equation}
vright_{tar} = v_{tar} - c_{\alpha} (D_l - D_r)
\end{equation}

@@

$d_0$ is a constant offset. $c_v$ and $c_{\alpha}$ are constant coefficients used for calibration.

@@

1) Rotating the vehicle around the center point of the axis that connects its front wheels in order to aim at the subject.

2) Go forward in a straight line until the vehicle is at the expected distance to the subject or the vehicle is not moving in the direction of the subject.

The algorithm is detailed in Algorithm~\ref{alg:rotateandgoalg}.  The variable $V_r$ is the speed at which the vehicle will rotate on its axis, and $V_f$ is the speed at which the vehicle will move forward once it can move on the subject's direction.

@@

A model of the proposed design was first built on Webots application.  The threading mechanism was implemented using virtual threads~\cite{Rekleitis2001}.  The leader traveled according to a predefined path with constant velocity, followiing the lemniscata trajectory.

@@

A tracked marker was placed in each side of the robot (on top of each thread reel). The human leader used his hand to grab the tip at which the two tethers were tied together. A third marker was placed in his hand, using a glove. The lemniscate of Gerono, used in the simulation, was drawn in the floor, and the human leader tried to move his hand following this shape as close as possible, with stable speed.  The shape was marked according to the shape described in Equation~\ref{eq:lemniscata}, using $a = 2$ [m].

The three markers allowed us to measure the trajectory of both the robot and the leader, and then obtain the same metrics calculated in the simulation.  Four experiments were performed for each set of parameter configurations.  In this case, only two set of configuration were tested for each strategy.

>>>>

On the other hand, several assistance devices for COPD treatments have been proposed.  Particularly relevant are novel telemedice applications to enhance complementary rehabiliation exercise at home that can track biological markers for patients~\cite{Yang2018,Wu2012}.  The work presented here follows the line established by \cite{Endo2015}.  Authors studied the use of a single thread tethered follower robot for home oxygen therapy, and compared two different control algorithms and their effectiveness to mimic the leader path and to avoid obstacles.  However, their approach focuses on the usage of the device exclusively for home therapy, and not within the context of a Pulmonary Rehabilitation procedure performed by medical personnel on medical facilities.

@@

The Raspberry Pi board connects to a WiFi network and can receive remote commands to control the robot. It also broadcasts telemetry data to any listening devices on the network. The control algorithms run in this board, which continuously communicates with the Arduino board to receive sensor data and to issue commands to move the motors or retract the reels.   The algorithms are programmed in python 3.7, which allows the exact same code to run both the simulated and real world prototype.

@@

%\subsection{Software Components}

@@

This control strategy is similar to the one presented in \cite{Ortlieb2016}. It is based on the idea that the difference in length between both threads provides a quasi-linear function of the relative angle between the subject and the vehicle orientation and, additionally, the mean of both thread length allows to approximate the relative distance between the robot and the subject.  They are described by Equations~\ref{eq:lemniscata}, \ref{eq:lemniscata2} and~\ref{eq:lemniscata3}.

@@

\begin{equation}
vleft_{tar} = v_{tar} + c_{\alpha} (D_l - D_r)
\label{eq:lemniscata2}
\end{equation}

\begin{equation}
vright_{tar} = v_{tar} - c_{\alpha} (D_l - D_r)
\label{eq:lemniscata3}
\end{equation}

\noindent where  $c_v$ and $c_{\alpha}$ are constant coefficients used for calibration.  As shown in Figure~\ref{fig:follow_params}, reel encoder information is $D_l$ and $D_r$ for the left and right reel, and finally $vleft_{tar}$ are $vright_{tar}$ are the power values that are directly used to drive power to each wheel motor.

@@

\noindent where $d_0$ is a constant offset that is used to customized the length of the thread where the robot does not move.

@@

\begin{itemize}
\item Rotating the vehicle around the center point of the axis that connects its front wheels in order to aim at the subject.
\item Go forward in a straight line until the vehicle is at the expected distance to the subject or the vehicle is not moving in the direction of the subject.
\end{itemize}

The procedure is detailed in Algorithm~\ref{alg:rotateandgoalg}.  The variable $V_r$ is the speed at which the vehicle will rotate on its axis, and $V_f$ is the speed at which the vehicle will move forward once it can move on the subject's direction.  The algorithm requires three parameters, $c_v$ and $c_r$ that regulates the coefficients for the forward and rotation movement, and an additional parameter $Dt_off$ that regulates the sensibility of the rotation movement.

@@

A model of the proposed design was first built on Webots~\cite{Michel2004} simulator.  The threading mechanism was implemented using virtual threads~\cite{Rekleitis2001}.  The leader traveled according to a predefined path with constant velocity, followiing the lemniscata trajectory.

@@

A tracked marker was placed in each side of the robot (on top of each thread reel). The human leader used his hand to grab the tip at which the two tethers were tied together. A third marker was placed in his hand, using a glove. The lemniscate of Gerono, used in the simulation, was marked on the floor, and the human leader tried to move his hand following this shape as close as possible, with stable speed.  The shape was marked according to the shape described in Equation~\ref{eq:lemniscata}, using $a = 2$ [m].

The three markers allowed to measure the trajectory of both the robot and the leader, and then obtain the same metrics calculated in the simulation.  Four experiments were performed for each set of parameter configurations.  In this case, only two set of configuration were tested for each strategy.
